The Speed of Evolution in a Two Dimensional Trait Space

### 2016-12-02 manuscript.tex
more changes made to methods section

%-----------------------------------------------------------------------------------------
\section*{Methods}
Our model describes the simultaneous evolution of two traits in asexual populations with no recombination, whose size $N$ is large but fixed.  We consider only beneficial mutations in our framework which occur at a rate $U_i$, for i=1,2.  A beneficial mutation modifying trait $i$ provides a fixed incremental gain $\Delta c_i$, in the relative fitness of a mutant.

Our model describes the simultaneous evolution of two traits (or loci) in an asexual population with no recombination.  The population size is taken to be large but fixed and finite.  Each trait evolves in the concurrent mutations regime, which

>>>>

%-----------------------------------------------------------------------------------------
\section*{Methods}
Our model describes the simultaneous evolution of two traits (or loci) in an asexual population with no recombination.  The population size $N$ is assumed to large but fixed.  We consider only beneficial mutations in our framework which occur at a rate $U_k$, where $k=1,2$ designates the trait.  A beneficial mutation modifying trait $k$ provides a fixed incremental gain $\Delta c_k$, in the relative fitness of a mutant.  No distinction is made between the types of beneficial mutations, and fitness is strictly determined by the number of benenficial mutations in the genotype of an individual.  Its relative fitness is given as its growth rate in excess of the population's mean growth rate $r_{i,j}-\bar{r}$, where $r_{i,j}=1+\Delta c_1 i + \Delta c_2 j$.

The populutation is divided into subpopulations consisting of fitness classes, whose frequencies are designated by $p_{i,j}$ with $i$ consists
